Formulating and Validating RDF Constraints Generically

### 2015-02-12 paper/paper 2/paper 2.tex
paper 2 - evaluation

We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
If a constraint cannot be expressed in DL, we only added the mapping to the generic constraint.
Therefore, we show that each constraint can be mapped to a generic constraint.
The following table shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraints:

\begin{evaluation-generic-overview}
Property Constraints & 48 & 65 (64.86) \\
Class Constraints & 17 & 23 (22.96) \\
Property and Class Constraints & 9 & 12 (12.16) \\
\hline
Simple Constraints & 46 & 62 (62.16) \\
Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
Complex Constraints & 18 & 24 (24.32) \\
\hline
DL Expressible & 51 & 69 (68.92) \\
DL Not Expressible & 23 & 31 (31.08) \\
\hline
Total & 74 & 100 \\
\end{evaluation-generic-overview}

Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
Two thirds of the total amount of constraints are property constraints, one fifth are class constraints, and approx. 10\% are composed of both property and class constraints.
Constraints may be either atomic (\ms{simple constraints}) or created out of simple and/or complex constraints (\ms{complex constraints}).
Almost two thirds are simple constraints, a quarter are complex constraints.
Almost 15 percent are complex constraints which can be formulated as simple constraints when using them in terms of syntactic sugar.
Constraints can either be expressible in DL or not.
The majority - nearly 70\% - of the overall constraints are expressible in DL.

>>>>

We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type.
We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages).
This technical report also contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
If a constraint type can be expressed in DL, we added the mapping to DL and to the \emph{generic constraint}.
If a constraint type cannot be expressed in DL, we only added the mapping to the \emph{generic constraint}.
Therefore, we show that each constraint type can be mapped to a \emph{generic constraint}.
Table \ref{tab:evaluation} shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraint types \emph{context}, \emph{complexity}, and \emph{DL expressivity}:

%\begin{evaluation-generic-overview}
%\emph{Property Constraints} & 48 & 65 (64.86) \\
%\emph{Class Constraints} & 17 & 23 (22.96) \\
%\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
%\hline
%\emph{Simple Constraints} & 46 & 62 (62.16) \\
%\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
%\emph{Complex Constraints} & 18 & 24 (24.32) \\
%\hline
%\emph{DL Expressible} & 51 & 69 (68.92) \\
%\emph{DL Not Expressible} & 23 & 31 (31.08) \\
%\hline
%Total & 74 & 100 \\
%\end{evaluation-generic-overview}

\begin{table}
  %\scriptsize
  %\sffamily
  \vspace{0cm}
	\centering
		\begin{tabular}{l|c|c}
      \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
      \hline
\emph{Property Constraints} & 48 & 65 (64.86) \\
\emph{Class Constraints} & 17 & 23 (22.96) \\
\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
\hline
\emph{Simple Constraints} & 46 & 62 (62.16) \\
\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
\emph{Complex Constraints} & 18 & 24 (24.32) \\
\hline
\emph{DL Expressible} & 51 & 69 (68.92) \\
\emph{DL Not Expressible} & 23 & 31 (31.08) \\
\hline
Total & 74 & 100 \\
		\end{tabular}
	\caption{Evaluation}
	\label{tab:evaluation}
\end{table}

%\newenvironment{evaluation-generic-overview}{
  %%\scriptsize
  %%\sffamily
  %\vspace{0cm}
	%\begin{center}
  %\begin{tabular}{l|c|c}
  %\hline
  %\textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
  %\hline
%
%}{
  %\hline
  %\end{tabular}
  %%\linebreak
	%\end{center}
%}

Constraints types can be classified as \emph{property constraints} and \emph{class constraints} (classification dimension \emph{context}).
Two thirds of the total amount of constraint types are \emph{property constraints} (e.g. \emph{existential} and \emph{universal quantification}), one fifth are \emph{class constraints} (e.g. \emph{allowed values}\footnote{Corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
\emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for literals and objects), and approx. 10\% are composed of both \emph{property and class constraints} (e.g. \emph{context-specific exclusive or of property groups}).
Constraint types may be either atomic (\emph{simple constraints}) or created out of \emph{simple} and/or \emph{complex constraints} (\emph{complex constraints}) (classification dimension \emph{complexity}).
Almost two thirds of the constraint types are \emph{simple constraints} (e.g. \emph{object property paths}), a quarter are \emph{complex constraints} (e.g. \emph{ranges of literal values}\footnote{Corresponds to \emph{R-45-RANGES-OF-RDF-LITERAL-VALUES}}), and
nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar (e.g. \emph{(un)qualified cardinality restrictions}).
Constraint types can either be \emph{expressible in DL} or \emph{not} (classification dimension \emph{DL expressivity}).
The majority - nearly 70\% - of the overall constraint types are expressible in DL.	
\emph{Literal pattern matching} is an example of a constraint type which cannot be represented in DL.
\tb{examples}
